\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-01-24 gwnnDraft02.tex
Fixed the figure names
Fixed missing units in section 3.
Found another typo.

We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}. First, due to the parameters of each sector being taken to be identical save for the Higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale. Using the one-loop running, the $\beta$ function can be solved:
\begin{equation}\label{eqn:QCDrunningi}
\alpha_{s}^i (\mu) = \frac{2\pi}{11-\frac{2n^i_f}{3}}\frac{1}{\ln{\mu/\Lambda^i}},
\end{equation}
where $n_f^i$ is the number of quark flavours with mass less than $\mu/2$ and $\Lambda^i$ is the scale where it would confine if all quarks remain massless. In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}. 
Because we have set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors. However, since the masses of the quarks in each sector are different, we end up with a unique running of the coupling for each sector. At every quark mass threshold for a given sector, we match the coupling strengths above and below the threshold and determine the new $\Lambda^i$ for the lower scale. For example, at the mass of the top quark, we match a five flavour coupling with the six flavour one:
\begin{equation}
\alpha_s^{i(5)}(2 m^i_t) = \alpha_s^{i(6)}(2 m^i_t) 
\end{equation} 
and thus
\begin{equation}
\Lambda_{(5)}^i = (m_t^{i})^{2/23}(\Lambda_{(6)}^i)^{21/23}.
\end{equation}
Suppressing the $i$'s for notational cleanliness, we can arrive at similar relations at the bottom and charm thresholds
\begin{equation}
\begin{split}
\Lambda_{(4)} = (m_b)^{2/25}(\Lambda_{(5)})^{23/25},
\\
\Lambda_{(3)} = (m_c)^{2/23}(\Lambda_{(4)})^{25/27}.
\end{split}
\end{equation}
These can be combined to show that
\begin{equation}
\Lambda_{(3)} = (m_t m_b m_c)^{2/27}(\Lambda_{(6)})^{21/27}.
\end{equation}
This type of matching procedure can be done as many times as necessary for a given sector. The process terminates when $\Lambda_i$ for a given scale is larger than the next quark mass threshold (i.e running the scale down arrives at the $\Lambda_{QCD}$ phase transition before reaching the next quark mass scale).
In cosmological terms, we can envision a sector's thermal history unfolding, whereas the plasma cools below each quark mass threshold and said quarks are frozen out. At a certain point, the sector arrives at the QCD phase transition and confinement occurs --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.

@@

\section{Reheating $N$ Sectors}
\label{sec:reheat}
%\begin{figure*}[tb]
%\centering
%\begin{minipage}[c]{\textwidth}
%\includegraphics[width=0.4\textwidth]{standardDecay.eps}
%\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
%\end{minipage}
%\hfill
%\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$. The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions. The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
%}
%\label{fig:reheatonDecays}
%\end{figure*}
A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$). Here we review the results of~\cite{Arkani-Hamed:2016rle}. Reheating occurs through the introduction a ``reheaton'' field. After inflation, the reheaton field possess the majority of the energy density of the Universe. Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$. Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth ]{MaxSW.png}
\hfill
\includegraphics[width=.45\textwidth]{LargeSW.png} 
\hfill
\includegraphics[width=.45\textwidth]{MedSW.png} 
\hfill
\includegraphics[width=.45\textwidth]{FiveSW.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave spectral energy density for the various scenarios found in Tab.~(\ref{tab:cases}).  All contributions are assumed to be from a non-runaway phase transition with terminal velocity $v = 0.95$. The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ . The shaded curves are the same as Fig.~\ref{fig::Nnatural}. In contrast to the runaway case, most scenarios evade the projected sensistivies of future experiments and therefore is the less optimal situation }
\label{fig:Haasw}
\end{figure*}

>>>>

We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}. First, due to the parameters of each sector being taken to be identical save for the Higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale. Using the one-loop running, the $\beta$ function can be solved:
\begin{equation}\label{eqn:QCDrunningi}
\alpha_{s}^i (\mu) = \frac{2\pi}{11-\frac{2n^i_f}{3}}\frac{1}{\ln{\mu/\Lambda^i}},
\end{equation}
where $n_f^i$ is the number of quark flavours with mass less than $\mu/2$ and $\Lambda^i$ is the scale where it would confine if all quarks remain massless. In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ MeV in $\overline{MS}$~\cite{PhysRevD.98.030001}. 
Because we have set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors. However, since the masses of the quarks in each sector are different, we end up with a unique running of the coupling for each sector. At every quark mass threshold for a given sector, we match the coupling strengths above and below the threshold and determine the new $\Lambda^i$ for the lower scale. For example, at the mass of the top quark, we match a five flavour coupling with the six flavour one:
\begin{equation}
\alpha_s^{i(5)}(2 m^i_t) = \alpha_s^{i(6)}(2 m^i_t) 
\end{equation} 
and thus
\begin{equation}
\Lambda_{(5)}^i = (m_t^{i})^{2/23}(\Lambda_{(6)}^i)^{21/23}.
\end{equation}
Suppressing the $i$'s for notational cleanliness, we can arrive at similar relations at the bottom and charm thresholds
\begin{equation}
\begin{split}
\Lambda_{(4)} = (m_b)^{2/25}(\Lambda_{(5)})^{23/25},
\\
\Lambda_{(3)} = (m_c)^{2/23}(\Lambda_{(4)})^{25/27}.
\end{split}
\end{equation}
These can be combined to show that
\begin{equation}
\Lambda_{(3)} = (m_t m_b m_c)^{2/27}(\Lambda_{(6)})^{21/27}.
\end{equation}
This type of matching procedure can be done as many times as necessary for a given sector. The process terminates when $\Lambda_i$ for a given scale is larger than the next quark mass threshold (i.e running the scale down arrives at the $\Lambda_{QCD}$ phase transition before reaching the next quark mass scale).
In cosmological terms, we can envision a sector's thermal history unfolding, whereas the plasma cools below each quark mass threshold and said quarks are frozen out. At a certain point, the sector arrives at the QCD phase transition and confinement occurs --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.

@@

\section{Reheating $N$ Sectors}
\label{sec:reheat}
%\begin{figure*}[tb]
%\centering
%\begin{minipage}[c]{\textwidth}
%\includegraphics[width=0.4\textwidth]{standardDecay.eps}
%\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
%\end{minipage}
%\hfill
%\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$. The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions. The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
%}
%\label{fig:reheatonDecays}
%\end{figure*}
A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$). Here we review the results of~\cite{Arkani-Hamed:2016rle}. Reheating occurs through the introduction a ``reheaton'' field. After inflation, the reheaton field possesses the majority of the energy density of the Universe. Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$. Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth ]{MaxSW.png}
\hfill
\includegraphics[width=.45\textwidth]{largeSW.png} 
\hfill
\includegraphics[width=.45\textwidth]{MedSW.png} 
\hfill
\includegraphics[width=.45\textwidth]{fiveSW.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave spectral energy density for the various scenarios found in Tab.~(\ref{tab:cases}).  All contributions are assumed to be from a non-runaway phase transition with terminal velocity $v = 0.95$. The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ . The shaded curves are the same as Fig.~\ref{fig::Nnatural}. In contrast to the runaway case, most scenarios evade the projected sensistivies of future experiments and therefore is the less optimal situation }
\label{fig:Haasw}
\end{figure*}
